% -*- root: Dissertation.tex -*-
\documentclass[Dissertation.tex]{subfiles} 
\begin{document}

\clearpage
\pagebreak
\newpage

\chapter{General Ps-H Formalism}
\label{chp:General}

\todoi{Combine with Chapter 3?} 

\lettrine{\textcolor{startcolor}{F}}{or} the first two partial waves of the Ps-H system, I was able to compare my code and results, including individual matrix elements, with code previously written by Peter Van Reeth. As there was no available code to compare against for the D-wave, we took steps to write a general code to compare against. The long-range code, covered in section \ref{sec:GeneralLong}, is a straightforward generalization from the previous codes. The short-range code, discussed in section \ref{sec:GeneralShort}, uses a different formalism, enabling us to compare two different methods.

\section{General Long-Range}
\label{sec:GeneralLong}

If the ``mixed terms'' in \cref{sec:MixedTerms} are not included for the D-wave, the P-wave and D-wave long-range codebases are very similar. The S-wave is not much different as well, but it only has a single symmetry.

\subsection{Long-Long}
\label{sec:GeneralLongLong}
\todoi{$\widetilde{S}$ and $\widetilde{C}$}
One major difference for similar matrix elements is the angular integrations. As shown in Appendix \ref{chp:AngularInt}, the external angular integrations for each partial wave have different results, due to the different spherical harmonics. $\bar{S}$ and $\bar{C}$ are also of a similar form between the partial waves, as seen in equations \ref{eq:PWaveSandCBar}, \ref{eq:PWaveSandC}, \ref{eq:DWaveSandCBar} and \ref{eq:DWaveSandC}. Other than the spherical harmonics, the spherical Bessel functions are different, as is the shielding function for $\bar{C}$. The spherical Bessel functions are easily called through the GNU Scientific Library \cite{GSL} for any $\ell$-value. The power of the shielding function varies as $m_\ell \geq (2\ell + 1)$. All of this allows us to easily generalize the long-long integrations.

%From \cref{eq:PartialWaveShielding}, the general shielding function for $\widetilde{C}$ to keep it regular at the origin is given by
%\begin{equation}
  %%\label{eq:PartialWaveShielding}
  %f_\ell(\rho) = \left[1 - \ee^{-\mu \rho} \left(1+\frac{\mu}{2}\rho\right)
  %\right]^{m_\ell}.
%\end{equation}
%From \cref{}, the derivatives $f_\ell^\prime(\rho)$ and $f_\ell^{\prime\prime}(\rho)$ are needed. In the \emph{Mathematica} notebook ``General Shielding Function.nb'', I found out that the derivatives can be written generally as
%\beq
%\label{eq:Shielding1Der}
%f_\ell^\prime(\rho) = -\frac{\mu m_\ell (\mu  \rho +1) \left[1-\frac{1}{2} e^{-\mu  \rho } (\mu  \rho +2)\right]^{m_\ell}}{\mu  \rho -2 e^{\mu  \rho }+2}
%\eeq
%and
%\beq
%\label{eq:Shielding1Der}
%f_\ell^{\prime\prime}(\rho) = \frac{\mu^2 m_\ell \left[-2 \mu  \rho  e^{\mu  \rho }+ m_\ell (\mu  \rho +1)^2-1\right] \left[1-\frac{1}{2} e^{-\mu  \rho } (\mu  \rho +2)\right]^{m_\ell}} {\left(\mu  \rho -2 e^{\mu  \rho }+2\right)^2}.
%\eeq


\subsection{Short-Long}
\label{sec:GeneralShortLong}
The short-range functions are also easily generalizable. For the P-wave and D-wave, these are seen in equations \ref{eq:PWavePhiBar} and \ref{eq:DWavePhiBar}. The $\phi_i$ and $\phi_j$ parts for each are the same. This fact can only be easily used for the short-long calculations and not the short-short calculations, due to the action of the $L$-operator on these terms. The formalism we have used for the short-long terms at every stage only operates $\mathcal{L}$ on the long-range parts. Section \ref{sec:GeneralShort} covers the calculations of the short-short terms using a general formalism.

\subsection{Implementation}
\label{sec:GeneralLongImp}



\section{General Short-Range}
\label{sec:GeneralShort}

\todoi{Look at Harris paper \cite{Harris2009}. \cite{Harris2005a}}

The short-range--short-range integrals are complicated more due to the 
gradient-gradient formalism we have used (see equation \ref{eq:BoundGradient}).
As an example of the nature of these, refer to\cref{sec:DWaveShortShort}.
The derivations were previously performed by rotating 
the coordinate system and integrating over external angles first, as 
described in Appendix \ref{chp:AngularInt}. This approach works, but it 
cannot be extended to higher partial waves without completing a full 
derivation for each partial wave. This also introduces terms that may be too 
singular for higher partial waves. Drake and Yan \cite{Yan1997} expand upon 
their previous work for the three-electron Hylleraas integrals to include the 
spherical harmonics. It is this approach that we take here. All equations 
used from their paper have been rederived in my notes.

\todoi{Point out that very slow compared to previous codes}

\subsection{Hamiltonian}
\label{sec:GenShortHam}
As we have for the bound state problem, the Hamiltonian is given compactly
as in \cref{eq:BoundHamiltonian} by
\beq
\label{eq:GenHam1}
H = \sum_{i=1}^3 \left(-\frac{1}{2} \nabla_i^2 - \frac{1}{r_i} \right) + \sum_{i>j}^3 \frac{1}{r_{ij}}.
\eeq

\noindent As worked out in my notes and shown in their paper, when the Laplacians are expanded, this is given by the form
\begin{align}
\label{eq:GenHam2}
\nonumber H = -\frac{1}{2} & \left[ \sum_{i=1}^3 \left( \frac{\partial^2}{\partial r_i^2} + \frac{2}{r_i} \frac{\partial}{\partial r_i} - \frac{\ell(\ell+1)}{r_i^2} \right) + \sum_{i>j}^3 \left( 2 \frac{\partial^2}{\partial r_i^2} + \frac{4}{r_{ij}} \frac{\partial}{\partial r_i} \right) + \sum_{i \neq j}^3 \left(\frac{r_i^2 - r_j^2 + r_{12}^2}{r_i r_j} \right) \right. \\
\nonumber &  \left. + \frac{r_{12}^2 + r_{13}^2 - r_{23}^2}{r_{12} r_{13}} \frac{\partial^2}{\partial r_{12} \partial r_{13}} + \frac{r_{12}^2 + r_{23}^2 - r_{13}^2}{r_{12} r_{23}} \frac{\partial^2}{\partial r_{12} \partial r_{23}} + \frac{r_{13}^2 + r_{23}^2 - r_{12}^2}{r_{13} r_{23}} \frac{\partial^2}{\partial r_{13} \partial r_{23}} \right. \\
& \left. + \sum_{i>j}^3 \frac{1}{r_{ij}} \frac{r_i}{r_j} \frac{\partial}{\partial r_{ij}} \left( \hat{\boldsymbol{r}_i} \cdot \hat{\nabla}_j^Y \right) + \sum_{i>j}^3 \frac{1}{r_{ji}} \frac{r_j}{r_i} \frac{\partial}{\partial r_{ji}} \left( \hat{\boldsymbol{r}_j} \cdot \hat{\nabla}_i^Y \right) \right]
\end{align}
% & \left. + \sum_{i>j}^3 \frac{1}{r_{ij}} \frac{r_i}{r_j} \frac{\partial}{\partial r_{ij}} \left( r_i^\hat \cdot \nabla_j^Y \right) \right]

\noindent This is the form when the mass polarization terms are unimportant
(with $\mu \rightarrow 0$). As defined in Ref. \cite{Yan1997},
$\hat{\boldsymbol{r}_j} = \boldsymbol{r}_i/r_i$ and $\hat{\nabla}_i^Y = r_i \nabla_i^Y$.
The terms involving $\nabla_i^Y$ only operate on the spherical 
harmonics, and they will be discussed in section \ref{sec:GenSphHarm}.

The wavefunction we use is slightly different from the form Drake and Yan 
use. Specifically, we handle the antisymmetrization operator differently in 
our code, and we do not include the $\Omega$ function, given by equation (10) 
in their paper. Part of the difference here is that we are working with two 
electrons and one positron, whereas they are working with systems that have 
three electrons, such as binding energy calculations of Li.

\subsection{General Integrals}
\label{sec:GenOverlap}
\todoi{Note that these shouldn't be conjugated, but for the short-range terms with $m = 0$, it does not matter. \pageref{BraNote}}
%As mentioned in the previous section, Drake and Yan's wavefunction is similar but not exactly the same. Thus, we cannot use the equations directly from their paper. Using their notation, the overlap integrals are given by
%\begin{align}
%\nonumber I^1(1) = \left< \phi_L^1 \left| \phi_R^1 \right. \right> = \sum_{\text{all } m_i^\prime m_i} & \int \mathrm{d}\boldsymbol{r}_1 \, \mathrm{d}\boldsymbol{r}_2 \, \mathrm{d}\boldsymbol{r}_3 \, r_1^{\tilde{j}_1} r_2^{\tilde{j}_2} r_3^{\tilde{j}_3} r_{12}^{\tilde{j}_{12}} r_{23}^{\tilde{j}_{23}} r_{31}^{\tilde{j}_{31}} \ee^{-(\tilde{\alpha} r_1 + \tilde{\beta} r_2 + \tilde{\gamma} r_3)} \\
%& \times Y_{\ell_1^\prime m_1^\prime}^* (\boldsymbol{r}_1) Y_{\ell_2^\prime m_2^\prime}^* (\boldsymbol{r}_2) Y_{\ell_3^\prime m_3^\prime}^* (\boldsymbol{r}_3) Y_{\ell_1 m_1} (\boldsymbol{r}_1) Y_{\ell_2 m_2} (\boldsymbol{r}_2) Y_{\ell_3 m_3} (\boldsymbol{r}_3).
%\end{align}
%This can be split into angular and radial parts, given by
%\begin{align}
%\nonumber I^1(1) = & \sum_{q_{12}=0}^{M_{12}} \sum_{q_{23}=0}^{M_{23}} \sum_{q_{31}=0}^{M_{31}} \sum_{k_{12}=0}^{L_{12}} \sum_{k_{23}=0}^{L_{23}} \sum_{k_{31}=0}^{L_{31}} C^1(1) \\
%& \times I_R \left(q_{12}, q_{23}, q_{31}, k_{12}, k_{23}, k_{31}; \tilde{j}_1, \tilde{j}_2, \tilde{j}_3, \tilde{j}_{12}, \tilde{j}_{23}, \tilde{j}_{31}; \tilde{\alpha}, \tilde{\beta}, \tilde{\gamma} \right),
%\end{align}
%where $\tilde{j}_1 = j_1^\prime + j_1$, etc. The $I_R$ function is only dependent on the radial coordinates and is given by equation (30) of their paper. The $C^1(1)$ function differs from theirs, as we do not have the 3j symbols in their $\Omega$ function. This is given in two parts as
%\begin{align}
%\nonumber C^1(1) =\, & (-1)^{q_{12} + q_{23} + q_{31}} \left(\ell_1^\prime,\ell_2^\prime,\ell_3^\prime,\ell_1,\ell_2,\ell_3 \right)^{1/2} \sum_{n_1 n_2 n_3} (n_1,n_2,n_3) \ThreeJSymbol{\ell_1^\prime,0}{\ell_1,0}{n_1,0}  \\
%& \times \ThreeJSymbol{\ell_2^\prime,0}{\ell_2,0}{n_2,0} \ThreeJSymbol{\ell_3^\prime,0}{\ell_3,0}{n_3,0} \ThreeJSymbol{q_{31},0}{q_{12},0}{n_1,0} \ThreeJSymbol{q_{12},0}{q_{23},0}{n_2,0} \nonumber \\
%& \times \ThreeJSymbol{q_{23},0}{q_{31},0}{n_3,0} \SixJSymbol{n_1,n_2,n_3}{q_{23},q_{31},q_{12}} \tilde{C}^1(1)
%\end{align}
%\noindent and
%\begin{align}
%\tilde{C}^1(1) = & \sum_{\text{all } m_i^\prime m_i t_i} (-1)^{m_1 + m_2 + m_3} \ThreeJSymbol{n_1,t_1}{n_2,t_2}{n_3,t_3} \nonumber \\
%& \times \ThreeJSymbol{l_1^\prime,-m_1^\prime}{l_1,m_1}{n_1,t_1} \ThreeJSymbol{l_2^\prime,-m_2^\prime}{l_2,m_2}{n_2,t_2} \ThreeJSymbol{l_1^\prime,-m_1^\prime}{l_3,m_3}{n_3,t_3}.
%\end{align}
%From the selection rules for the 3j symbol, $t_i = m_i^\prime - m_i$. The factor $(2\ell+1)$ appears often in these types of derivations, so we adopt the shorthand notation of $(l,m,n,\ldots) = (2l+1)(2m+1)(2n+1) \ldots$.

Using the notation in Ref.~\cite{Yan1997}, the terms in \cref{eq:GenHam2} without the spherical harmonic operator, $\hat{\nabla}_i^Y$, will be of the general form
\begin{align}
\label{eq:ShortIntGen}
\nonumber I(\ell_1^\prime m_1^\prime, \ell_2^\prime m_2^\prime, &\ell_3^\prime m_3^\prime, \ell_1 m_1, \ell_2 m_2, \ell_3 m_3; j_1,j_2,j_3,j_{12},j_{23},j_{31}; \alpha, \beta, \gamma) \\
= & \; \int d \textit{\textbf{r}}_1 d \textit{\textbf{r}}_2 d \textit{\textbf{r}}_3
r_1^{j_1} r_2^{j_2} r_3^{j_3} r_{12}^{j_{12}}
r_{23}^{j_{23}} r_{31}^{j_{31}}
e^{-(\alpha r_1 + \beta r_2 + \gamma r_3)}  \nonumber \\
& \times Y_{\ell_1^\prime m_1^\prime}^* (\textit{\textbf{r}}_1) Y_{\ell_2^\prime m_2^\prime}^* (\textit{\textbf{r}}_2) Y_{\ell_3^\prime m_3^\prime}^* (\textit{\textbf{r}}_3) Y_{\ell_1 m_1} (\textit{\textbf{r}}_1) Y_{\ell_2 m_2} (\textit{\textbf{r}}_2) Y_{\ell_3 m_3} (\textit{\textbf{r}}_3)\, .
\end{align}
Note that $\alpha$, $\beta$, and $\gamma$ are not necessarily the same as those
in \cref{eq:PhiDef}. These will be $2\alpha$, $2\beta$, and $2\gamma$ for the
direct-direct terms and $2\alpha$, $\beta+\gamma$, $\gamma+\beta$ for the
direct-exchange terms. After some manipulation, this integral can be written as
\begin{align}
\label{eq:ShortIntGen2}
I(\ell_1^\prime m_1^\prime, &\ell_2^\prime m_2^\prime, \ell_3^\prime m_3^\prime, \ell_1 m_1, \ell_2 m_2, \ell_3 m_3; j_1,j_2,j_3,j_{12},j_{23},j_{31}; \alpha, \beta, \gamma)  \nonumber \\
= & \; \sum_{q_{12}=0}^{M_{12}} \sum_{q_{23}=0}^{M_{23}} \sum_{q_{31}=0}^{M_{31}} \sum_{k_{12}=0}^{L_{12}} \sum_{k_{23}=0}^{L_{23}} \sum_{k_{31}=0}^{L_{31}}  \nonumber \\
& \times I_{\rm{ang}}(\ell_1^\prime m_1^\prime, \ell_2^\prime m_2^\prime, \ell_3^\prime m_3^\prime, \ell_1 m_1, \ell_2 m_2, \ell_3 m_3; q_{12}, q_{23}, q_{31})  \nonumber \\
& \times I_{\rm{R}}(q_{12}, q_{23}, q_{31}, k_{12}, k_{23}, k_{31}; j_1, j_2, j_3, j_{12}, j_{23}, j_{31}; \alpha, \beta, \gamma).
\end{align}
For even values of $j_{12}$, $M_{12} = \frac{1}{2}j_{12}$ and $L_{12} = \frac{1}{2}j_{12} - q_{12}$. For odd values of $j_{12}$, $M_{12} = \infty$ and $L_{12} = \frac{1}{2}(j_{12}+1)$. The same type of upper limits apply to the $j_{23}$ and $j_{31}$ terms.

The angular part of $I$ is given by
\begin{align}
\label{eq:DrakeGenAng}
I_{\rm{ang}}(\ell_1^\prime m_1^\prime, & \ell_2^\prime m_2^\prime, \ell_3^\prime m_3^\prime, \ell_1 m_1, \ell_2 m_2, \ell_3 m_3; q_{12}, q_{23}, q_{31})  \nonumber \\
= & \;(-1)^{m_1^\prime + m_2^\prime + m_3^\prime + q_{12} + q_{23} + q_{31}} (\ell_1^\prime, \ell_2^\prime, \ell_3^\prime, \ell_1, \ell_2, \ell_3)^{1/2} \sum_{n_1 n_2 n_3} (n_1,n_2,n_3)  \nonumber \\
& \times \SixJSymbol{n_1,n_2,n_3}{q_{23},q_{31},q_{12}} \ThreeJSymbol{n_1, m_1^\prime - m_1}{n_2, m_2^\prime - m_2}{n_3, m_3^\prime - m_3}  \nonumber \\
& \times \ThreeJSymbol{\ell_1^\prime,-m_1^\prime}{\ell_1,m_1}{n_1, m_1^\prime - m_1} \ThreeJSymbol{\ell_2^\prime,-m_2^\prime}{\ell_2,m_2}{n_2,m_2^\prime - m_2}  \nonumber \\
& \times \ThreeJSymbol{\ell_1^\prime,-m_1^\prime}{\ell_3,m_3}{n_3,m_3^\prime - m_3} \ThreeJSymbol{\ell_1^\prime,0}{\ell_1,0}{n_1,0} \ThreeJSymbol{\ell_2^\prime,0}{\ell_2,0}{n_2,0}  \nonumber \\
& \times \ThreeJSymbol{\ell_3^\prime,0}{\ell_3,0}{n_3,0} \ThreeJSymbol{q_{31},0}{q_{12},0}{n_1,0} \ThreeJSymbol{q_{12},0}{q_{23},0}{n_2,0} \ThreeJSymbol{q_{23},0}{q_{31},0}{n_3,0}.
\end{align}
This expression includes summations over both the Wigner 3-j and 6-j
coefficients \cite{Edmonds1996,Brink1993,Rose1995}, also known as the 3-j and
6-j symbols. The 3-j symbols are related to the Clebsch-Gordan coefficients by
\cite[p.46]{Edmonds1996}
\begin{equation}
\label{eq:Clebsch3J}
\ThreeJSymbol{j_1,m_1}{j_2,m_2}{j_3,m_3} = (-1)^{j_1 - j_2 + m_3} (2 j_3 + 1)^{-1/2} \ClebschGordon{j_1,m_1}{j_2,m_2}{j_3,-m_3}.
\end{equation}
The advantage of the 3-j symbols over the Clebsch-Gordan coefficients is that 
they are a more symmetric representation of angular momentum. The factor
$(2\ell+1)$ appears often in these types of derivations, so we adopt their 
shorthand notation of $(l,m,n,\ldots) = (2l+1)(2m+1)(2n+1) \cdots$.

The radial part of \cref{eq:ShortIntGen2} is 
\begin{align}
\label{eq:ShortGenIR}
I_{\rm{R}}(q_{12}, q_{23}, q_{31}&, k_{12}, k_{23}, k_{31}; j_1, j_2, j_3, j_{12}, j_{23}, j_{31}; \alpha, \beta, \gamma)  \nonumber \\
= & \; C_{j_{12} q_{12} k_{12}} C_{j_{23} q_{23} k_{23}} C_{j_{31} q_{31} k_{31}}  \nonumber \\
& \times W_{\rm{R}}(q_{12}, q_{23}, q_{31}, k_{12}, k_{23}, k_{31}; j_1, j_2, j_3, j_{12}, j_{23}, j_{31}; \alpha, \beta, \gamma).
\end{align}
The $C_{jqk}$ coefficients are the same as in \cref{eq:Ccoeff}. The $W_{\rm{R}}$ function is built from the $W$ functions in \cref{eq:Wfunc} as
\begin{align}
\label{eq:ShortGenWR}
W_{\rm{R}}(&q_{12}, q_{23}, q_{31}, k_{12}, k_{23}, k_{31}; j_1, j_2, j_3, j_{12}, j_{23}, j_{31}; \alpha, \beta, \gamma)  \nonumber \\
=\; \; & W(j_1 + 2 + s_{12} + s_{31}, j_2 + 2 + j_{12} - s_{12} + s_{23}, j_3 + 2 + j_{23} - s_{23} + j_{31} - s_{31}; \alpha, \beta, \gamma)  \nonumber \\
+ & W(j_1 + 2 + s_{12} + s_{31}, j_3 + 2 + s_{23} + j_{31} - s_{31}, j_2 + 2 + j_{12} - s_{12} + j_{23} - s_{23}; \alpha, \gamma, \beta)  \nonumber \\
+ & W(j_2 + 2 + s_{12} + s_{23}, j_1 + 2 + j_{12} - s_{12} + s_{31}, j_3 + 2 + j_{23} - s_{23} + j_{31} - s_{31}; \beta, \alpha, \gamma)  \nonumber \\
+ & W(j_2 + 2 + s_{12} + s_{23}, j_3 + 2 + j_{23} - s_{23} + s_{31}, j_1 + 2 + j_{12} - s_{12} + j_{31} - s_{31}; \beta, \gamma, \alpha)  \nonumber \\
+ & W(j_3 + 2 + s_{23} + s_{31}, j_1 + 2 + s_{12} + j_{31} - s_{31}, j_2 + 2 + j_{12} - s_{12} + j_{23} - s_{23}; \gamma, \alpha, \beta)  \nonumber \\
+ & W(j_3 + 2 + s_{23} + s_{31}, j_2 + 2 + s_{12} + j_{23} - s_{23}, j_1 + 2 + j_{12} - s_{12} + j_{31} - s_{31}; \gamma, \beta, \alpha),
\end{align}
with $s_{ij} = q_{ij} + 2 k_{ij}$.
Note that there are similarities with \cref{eq:FourBodyExpansion}.


\todoi{Mention \cite{Luscombe1998,Wei1998,Rasch2003} for possible speedups in this code.}


\subsection{Spherical Harmonic Terms}
\label{sec:GenSphHarm}

The terms in \cref{eq:GenHam2} involving the spherical harmonic operator
$\hat{\nabla}_i^Y$ have to be handled differently than the other terms. In
Ref.~\cite{Yan1997}, they do different permutations for the three-electron
problem, so for the $p$ in their paper, we always use $p = 1$.

\begin{align}
\label{eq:GenY12}
I^1(\hat{\boldsymbol{r}_1} \cdot \hat{\nabla}_2^Y) = &\sum_{q_{12}=0}^{M_{12}} \sum_{q_{23}=0}^{M_{23}} \sum_{q_{31}=0}^{M_{31}} \sum_{k_{12}=0}^{L_{12}} \sum_{k_{23}=0}^{L_{23}} \sum_{k_{31}=0}^{L_{31}} \sum_{T_1 T_2} b(\ell_2; T_2) C^1(\hat{\textit{\textbf{r}}}_1 \bm{\cdot} \hat{\textit{\textbf{r}}}_2)  \nonumber \\
& \times I_{\rm{R}}(q_{12}, q_{23}, q_{31}, k_{12}, k_{23}, k_{31}; j_1, j_2, j_3, j_{12}, j_{23}, j_{31}; \alpha, \beta, \gamma)
\end{align}
The $b$ function here is defined by
\begin{align}
\label{eq:bfunc}
b(\ell; \ell - 1) &= \ell + 1  \nonumber \\
b(\ell; \ell + 1) &= -\ell.
\end{align}
For any other values of the arguments, $b$ gives 0. $C^1$ is given by
\begin{align}
\label{eq:CP12}
C^1(\hat{\textit{\textbf{r}}}_1 & \bm{\cdot} \hat{\textit{\textbf{r}}}_2) = (\ell_1^\prime, \ell_2^\prime, \ell_3^\prime, \ell_1, \ell_2, \ell_3)^{1/2} (-1)^{q_{12} + q_{23} + q_{31}} \sum_{n_1 n_2 n_3} (n_1, n_2, n_3, T_1, T_2)  \nonumber \\
& \times \ThreeJSymbol{1,0}{\ell_1,0}{T_1,0} \ThreeJSymbol{1,0}{\ell_2,0}{T_1,0} \ThreeJSymbol{\ell_1^\prime,0}{T_1,0}{n_1,0} \ThreeJSymbol{\ell_2^\prime,0}{T_2,0}{n_2,0} \ThreeJSymbol{\ell_3^\prime,0}{\ell_3,0}{n_3,0}  \nonumber \\
& \times \ThreeJSymbol{q_{31},0}{q_{12},0}{n_1,0} \ThreeJSymbol{q_{12},0}{q_{23},0}{n_2,0} \ThreeJSymbol{q_{23},0}{q_{31},0}{n_3,0} \SixJSymbol{n_1,n_2,n_3}{q_{23},q_{31},q_{12}} \tilde{C}^1(\hat{\textit{\textbf{r}}}_1 \bm{\cdot} \hat{\textit{\textbf{r}}}_2),
\end{align}
with
\begin{align}
\label{eq:CPtilde12}
\tilde{C}^1(\hat{\textit{\textbf{r}}}_1 & \bm{\cdot} \hat{\textit{\textbf{r}}}_2) = \sum_\mu (-1)^{\mu-m_3} \ThreeJSymbol{1,\mu}{\ell_1,m_1}{T_1,-\mu-m_1} \ThreeJSymbol{1,-\mu}{\ell_2,m_2}{T_2,\mu-m_2}  \nonumber \\
& \times \ThreeJSymbol{\ell_3^\prime,-m_3^\prime}{\ell_3,m_3}{n_3,m_3^\prime-m_3} \ThreeJSymbol{\ell_1^\prime,-m_1^\prime}{T_1,\mu+m_1}{n_1,m_1^\prime-\mu-m_1}  \nonumber \\
& \times \ThreeJSymbol{\ell_2^\prime,-m_2^\prime}{T_2,-\mu+m_2}{n_2,m_2^\prime+\mu-m_2} \ThreeJSymbol{n_1,m_1^\prime-\mu-m_1}{n_2,m_2^\prime+\mu-m_2}{n_3,m_3^\prime-m_3}.
\end{align}
The values that $\mu$ can take are $-1$, $0$, and $1$.

Considering the properties of the 3-j symbols in \cref{eq:CPtilde12}, the 
limits for the $T_1$ summation in \cref{eq:GenY12} are $\abs{1 - \ell_1}$ to
$1 + \ell_1$. Similarly, for the $T_2$ summation, the limits are
$\abs{1 - \ell_2}$ to $1 + \ell_2$. However, considering that the $b$
function in \cref{eq:bfunc} can give 0, not all $T_2$ in this range are used.

Unlike the previous section, the expressions here are not exactly the same as 
that in Yan and Drake \cite{Yan1997}, since as noted, their wavefunction has 
an extra set of coefficients given by
\begin{align}
\Omega(\ell_1, \ell_2, \ell_{12}, &\ell_3, L, M_L, m_1, m_2, m_3) = (-1)^{\ell_1 - \ell_2 + m_{12} + \ell_{12} - \ell_3 + M_L} (\ell_{12}, L)^{1/2}  \nonumber \\
& \times \ThreeJSymbol{\ell_1, m_1}{\ell_2,m_2}{\ell_{12},-m_{12}} \ThreeJSymbol{\ell_{12},m_{12}}{\ell_3,m_3}{L,-M_L}.
\end{align}
This addition to their wavefunction is included in the
$\tilde{C}^1(\hat{\textit{\textbf{r}}}_1 \bm{\cdot} \hat{\textit{\textbf{r}}}_2)$
and allows them to reduce these using graphical methods as in
Refs.~\cite{Lindgren2012,Brink1993}. Unfortunately, such simplifications are not possible with the 
form of our wavefunction.

We note that $C^1(\hat{\textit{\textbf{r}}}_1 \bm{\cdot} \hat{\textit{\textbf{r}}}_2) = C^1(\hat{\textit{\textbf{r}}}_2 \bm{\cdot} \hat{\textit{\textbf{r}}}_1)$, but $I^1(\hat{\boldsymbol{r}_1} \cdot \hat{\nabla}_2^Y) \neq I^1(\hat{\boldsymbol{r}_2} \cdot \hat{\nabla}_1^Y)$. Namely,
\begin{align}
\label{eq:GenY21}
I^1(\hat{\boldsymbol{r}_2} \cdot \hat{\nabla}_1^Y) = &\sum_{q_{12}=0}^{M_{12}} \sum_{q_{23}=0}^{M_{23}} \sum_{q_{31}=0}^{M_{31}} \sum_{k_{12}=0}^{L_{12}} \sum_{k_{23}=0}^{L_{23}} \sum_{k_{31}=0}^{L_{31}} \sum_{T_1 T_2} b(\ell_1; T_1) C^1(\hat{\textit{\textbf{r}}}_1 \bm{\cdot} \hat{\textit{\textbf{r}}}_2)  \nonumber \\
& \times I_{\rm{R}}(q_{12}, q_{23}, q_{31}, k_{12}, k_{23}, k_{31}; j_1, j_2, j_3, j_{12}, j_{23}, j_{31}; \alpha, \beta, \gamma).
\end{align}
More generally, these integrals can be written as
\begin{align}
\label{eq:GenYij}
I^1(\hat{\boldsymbol{r}_i} \cdot \hat{\nabla}_j^Y) = &\sum_{q_{12}=0}^{M_{12}} \sum_{q_{23}=0}^{M_{23}} \sum_{q_{31}=0}^{M_{31}} \sum_{k_{12}=0}^{L_{12}} \sum_{k_{23}=0}^{L_{23}} \sum_{k_{31}=0}^{L_{31}} \sum_{T_i T_j} b(\ell_j; T_j) C^1(\hat{\textit{\textbf{r}}}_i \bm{\cdot} \hat{\textit{\textbf{r}}}_j)  \nonumber \\
& \times I_{\rm{R}}(q_{12}, q_{23}, q_{31}, k_{12}, k_{23}, k_{31}; j_1, j_2, j_3, j_{12}, j_{23}, j_{31}; \alpha, \beta, \gamma),
\end{align}
and $C^1(\hat{\textit{\textbf{r}}}_i \bm{\cdot} \hat{\textit{\textbf{r}}}_j) = C^1(\hat{\textit{\textbf{r}}}_j \bm{\cdot} \hat{\textit{\textbf{r}}}_i)$. Using cyclic permutations,
\begin{align}
\label{eq:CP23}
C^1(\hat{\textit{\textbf{r}}}_2 & \bm{\cdot} \hat{\textit{\textbf{r}}}_3) = (\ell_1^\prime, \ell_2^\prime, \ell_3^\prime, \ell_1, \ell_2, \ell_3)^{1/2} (-1)^{q_{12} + q_{23} + q_{31}} \sum_{n_1 n_2 n_3} (n_1, n_2, n_3, T_2, T_3)  \nonumber \\
& \times \ThreeJSymbol{1,0}{\ell_2,0}{T_2,0} \ThreeJSymbol{1,0}{\ell_3,0}{T_3,0} \ThreeJSymbol{\ell_1^\prime,0}{\ell_1,0}{n_1,0} \ThreeJSymbol{\ell_2^\prime,0}{T_2,0}{n_2,0} \ThreeJSymbol{\ell_3^\prime,0}{T_3,0}{n_3,0}  \nonumber \\
& \times \ThreeJSymbol{q_{31},0}{q_{12},0}{n_1,0} \ThreeJSymbol{q_{12},0}{q_{23},0}{n_2,0} \ThreeJSymbol{q_{23},0}{q_{31},0}{n_3,0} \SixJSymbol{n_1,n_2,n_3}{q_{23},q_{31},q_{12}} \tilde{C}^1(\hat{\textit{\textbf{r}}}_2 \bm{\cdot} \hat{\textit{\textbf{r}}}_3)
\end{align}
with
\begin{align}
\label{eq:CPtilde23}
\tilde{C}^1(\hat{\textit{\textbf{r}}}_2 & \bm{\cdot} \hat{\textit{\textbf{r}}}_3) = \sum_\mu (-1)^{\mu-m_1} \ThreeJSymbol{1,\mu}{\ell_2,m_2}{T_2,-\mu-m_2} \ThreeJSymbol{1,-\mu}{\ell_3,m_3}{T_3,\mu-m_3}  \nonumber \\
& \times \ThreeJSymbol{\ell_1^\prime,-m_1^\prime}{\ell_1,m_1}{n_1,m_1^\prime-m_1} \ThreeJSymbol{\ell_2^\prime,-m_2^\prime}{T_2,\mu+m_2}{n_2,m_2^\prime-\mu-m_2}  \nonumber \\
& \times \ThreeJSymbol{\ell_3^\prime,-m_3^\prime}{T_3,-\mu+m_3}{n_3,m_3^\prime+\mu-m_3} \ThreeJSymbol{n_1,m_1^\prime-m_1}{n_2,m_2^\prime-\mu-m_2}{n_3,m_3^\prime+\mu-m_3},
\end{align}
and
\begin{align}
\label{eq:CP31}
C^1(\hat{\textit{\textbf{r}}}_3 & \bm{\cdot} \hat{\textit{\textbf{r}}}_1) = (\ell_1^\prime, \ell_2^\prime, \ell_3^\prime, \ell_1, \ell_2, \ell_3)^{1/2} (-1)^{q_{12} + q_{23} + q_{31}} \sum_{n_1 n_2 n_3} (n_1, n_2, n_3, T_3, T_1)  \nonumber \\
& \times \ThreeJSymbol{1,0}{\ell_3,0}{T_3,0} \ThreeJSymbol{1,0}{\ell_1,0}{T_1,0} \ThreeJSymbol{\ell_2^\prime,0}{\ell_2,0}{n_2,0} \ThreeJSymbol{\ell_3^\prime,0}{T_3,0}{n_3,0} \ThreeJSymbol{\ell_1^\prime,0}{T_1,0}{n_1,0}  \nonumber \\
& \times \ThreeJSymbol{q_{31},0}{q_{12},0}{n_1,0} \ThreeJSymbol{q_{12},0}{q_{23},0}{n_2,0} \ThreeJSymbol{q_{23},0}{q_{31},0}{n_3,0} \SixJSymbol{n_1,n_2,n_3}{q_{23},q_{31},q_{12}} \tilde{C}^1(\hat{\textit{\textbf{r}}}_3 \bm{\cdot} \hat{\textit{\textbf{r}}}_1)
\end{align}
with
\begin{align}
\label{eq:CPtilde31}
\tilde{C}^1(\hat{\textit{\textbf{r}}}_3 & \bm{\cdot} \hat{\textit{\textbf{r}}}_1) = \sum_\mu (-1)^{\mu-m_2} \ThreeJSymbol{1,\mu}{\ell_3,m_3}{T_3,-\mu-m_3} \ThreeJSymbol{1,-\mu}{\ell_1,m_1}{T_1,\mu-m_1}  \nonumber \\
& \times \ThreeJSymbol{\ell_2^\prime,-m_2^\prime}{\ell_2,m_2}{n_2,m_2^\prime-m_2} \ThreeJSymbol{\ell_3^\prime,-m_3^\prime}{T_3,\mu+m_3}{n_3,m_3^\prime-\mu-m_3}  \nonumber \\
& \times \ThreeJSymbol{\ell_1^\prime,-m_1^\prime}{T_1,-\mu+m_1}{n_1,m_1^\prime+\mu-m_1} \ThreeJSymbol{n_1,m_1^\prime+\mu-m_1}{n_2,m_2^\prime-m_2}{n_3,m_3^\prime-\mu-m_3}.
\end{align}


\section{Program}
\label{sec:GenShortProg}
The 

\cref{eq:FourBodyExpansion}

\cref{eq:ShortIntGen2}

\cref{eq:GenYij}





\biblio
\end{document}