% -*- root: Dissertation.tex -*-
\documentclass[Dissertation.tex]{subfiles} 
\begin{document}

\chapter{W Function Limits}
\label{chp:WLimits}
%\todoi{Write this all in terms of $j_i$, $k_i$, $l_i$, etc. instead of $k_1$, $k_2$, $k_{12}$, etc.}
%\todoi{Get rid of all old equation environments.}

\lettrine{\textcolor{startcolor}{P}}{recalculating} the results of the W 
function yields significant improvements to the speed of this program.  The 
number of terms in the trial function increases greatly with increasing
$\omega$. The number of elements of the matrices Phi2HPhi and PhiPhi is
$N(\omega)^2$. Only half of each of these matrices need to be calculated, 
since the upper triangular portion mirrors the bottom triangle. However, we 
use the difference between the two triangles to check whether the short-short 
integrations are converged. The W function is called repeatedly for each 
element, but the parameters are not unique between elements of the matrices.

A four-dimensional matrix is constructed with ranges of all possible inputs 
to the W function, and the output of the W function is stored as the 
elements.  The range of the parameters to the W function needs to be 
determined so that no extra computation takes place for impossible inputs and 
that values are not read outside of the matrix. Also note that this Appendix
gives the powers of $r_i$ and $r_{ij}$ in the form given in the Drake and
Yan \cite{Drake1995} paper and not in the form given by \cref{eq:PhiDef}.

\section{\texorpdfstring{$\alpha$, $\beta$ and $\gamma$} {alpha, beta and gamma} Definitions}

The last three parameters of the W function are $\alpha$, $\beta$ and $\gamma$.
There are exactly six permutations of these parameters. All six of these 
occur in the T function for a set of l, m and n parameters. Since there are 
only six possibilities from equation (6) of Drake and Yan \cite{Drake1995}, 
the last dimension of the WMatrix is 6. If this fact was not used, a six-
dimensional matrix would have to be used.

\section{Limits of convergence on W}

The first three parameters of the W function are called $l$, $m$ and $n$
(in order). From \cite{Drake1995}, there are three conditions for the first
three parameters that determine whether W converges.
\[l \geq 0, ~~~~ l+m+1 \geq 0, ~~~~ l+m+n+2 \geq 0\]
The other limits that must be taken into account are that $j_{\mu \nu} \geq -1$
and $j_{\mu} \geq -2$. However, for this program, none of $j_{\mu \nu}$ or
$j_{\mu}$ are more singular than -1.  Also, the lower limits of $\omega$ and
$q$ are 0.

Note that since we are calculating the inner products of $\phi_i$ and $\phi_j$,
the upper limit on any of $j_{\mu \nu}$ and $j_{\mu}$ is $2\omega$, not
$\omega$.

\section{\emph{l} Parameter}
The first parameter, \emph{l}, is
\begin{equation}
	\label{l_Param}j_1 + 2 + 2q + 2 k_{12} + 2 k_{31}.
\end{equation}
\underline{Min}: Let $j_{12} = -1$, $j_{23} = j_{31} = 0$.  From this, we 
have the upper limits of the summations of equation () of \cite{Drake1995} as 
$k_{12} = \tfrac{1}{2} (j_{12} + 1) = 0$, $k_{23} = 0$ and $k_{31} = 0$. With 
$j_1$ as its minimum of -1 and the above conditions, this becomes 1.

\noindent\underline{Max}: Choosing $j_1 = 2 \omega$ and $j_{12} = j_{13} = -1$, \cref{l_Param} becomes $2 \omega + 2q + 4$.  This is the upper limit of $l$.

\section{\emph{m} Parameter}
The \emph{m} parameter is
\begin{equation}
	\label{m_Param}
	j_2 + 2 + j_{23} - 2 k_{23} + 2 k_{12}.
\end{equation}
\underline{Min}: 
We have to look at three conditions for this, which yield all the same result.
This is because the upper limits of the summations change if one of the
$j_{\mu \nu}$ or $j_{\mu}$ is even. This can be seen from Ref.~\cite{Perkins1969}.
\begin{itemize}
	\item $j_2$, $j_{23}$ and $j_{12}$ all odd. In this case, \cref{m_Param} becomes $j_2 + 2 + j_{12}.$ \\ If $j_2 = j_{12} = -1$, this equation becomes 0.
	\item $j_{23}$ is even. Then the upper limit of the summation becomes $\frac{j_{23}}{2}-q$ by \cite{Perkins1969}. If $j_{23} = 2 \omega$, then $\frac{j_{23}}{2}-q = \omega - q$.  Minimizing this by $\omega = 0$ and $q = 0$ gives
\begin{equation}
	j_2 + 2 + 2 k_{12} = j_2 + 2 + j_{12} + 1.
\end{equation}
	With $j_2 = j_{12} = -1$, this equation reduces to 1, giving a lower limit higher than the all odd case.
	\item $j_{12}$ is even. Then the summation upper limit is $\frac{j_{12}}{2}-q$ by \cite{Perkins1969}. \Cref{m_Param} becomes $j_2 + 2 + j_{23} - (j_{23}+1)$ if $q = j_{12} = 0$.  Setting $j_2$ as its minimum of -1 gives a lower limit of 0.
\end{itemize}
\underline{Max}: We have to examine the case of all $j_{\mu \nu}$ and
   $j_{\mu}$ being odd and the case of at least one being even.
\begin{itemize}
  \item If $j_{23}$ and $j_{31}$ are odd, \cref{m_Param} becomes
  \begin{equation}
    j_3 + 2 + j_{23} - 2 k_{23} + 2 k_{31} = j_3 + 2 + j_{23} - 2\cdot\tfrac{1}{2} (j_{23} + 1) + 2\cdot\tfrac{1}{2} (j_{31} + 1) = j_{3} + 2 + j_{31}.
  \end{equation}
If $j_3 = 2\omega - 1$ and $j_{31} = 1$, then this equation becomes $2\omega + 2$.  This is not the largest this parameter can be, which is given for the next case.
  \item If $j_{23} = 0$, \cref{m_Param} becomes
	\begin{equation}
	j_3 + 2 + j_{23} + 2\cdot\tfrac{1}{2}(j_{31}+1) = j_3 + 2 + j_{23} + j{31} + 1 = j_3 + j_{23} + j_{31} + 3.
	\end{equation}
  Note that this has no q-dependence, and the q summation is finite.  If one of $j_3$, $j_{23}$ or $j_{31}$ is $2\omega$, and the others are 0, then this becomes $2\omega + 3$.
\end{itemize}

\section{\emph{n} Parameter}
The \emph{n} parameter is
\begin{equation}
	\label{n_Param}j_1 + 2 + j_{12} - 2 q - 2 k_{12} + j_{31} - 2 k_{23}.
\end{equation}
\underline{Min}: If $j_{12}$ and $j_{31}$ are odd, then \cref{n_Param} becomes
	\begin{equation}
	j_1 + 2 + j_{12} - 2q - 2\cdot\tfrac{1}{2}(j_{12}+1) + j_{31} - 2\cdot\tfrac{1}{2}(j_{31}+1) = j_1 - 2q.
	\end{equation}
\underline{Max}: When $j_{12} = 0$, $k_{12} = 0$, \cref{n_Param} becomes
$j_2 + 2 + j_{12} + 2k_{23}$. Then if $j_2 = 2\omega$ or $j_{12} = 2\omega$,
this becomes $2\omega + 2$.  With the minimum of $j_1$ as -1, the lower limit
of the $n$ parameter is $-1 - 2q$.

\section{Summary}
\Cref{tab:WLimits} summarizes these results.

\begin{table}
\centering
\begin{tabular}{c c c}
\toprule
Parameter & Minimum & Maximum \\
\midrule
  l & 1 & $2\omega + 2q + 4$ \\
  m & 0 & $2\omega + 3$ \\
  n	& $-1 - 2q$ & $2\omega + 2$ \\
\bottomrule
\end{tabular}
\caption{W Function Limits Summary}
\label{tab:WLimits}
\end{table}




\biblio
\end{document}